\huge A Usability Evaluation of Tor Launcher

### 2017-03-21 pets2017-paper/pets2017-paper.tex
Flip the meaning of e# and e#' in \ref{states} (Appendix A).
Looking at the graph, it seems all the children of the "bridge no" edge
have the '.
Make caption of fig:digraph consistent.
start → first
add bridge help
doesn't show any "quit" states.

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{torconfig.pdf}
\caption{
A digraph illustrating the potential user paths through the interface. Non-leaf nodes are screens in the user interface (start, bridge 1, bridge 2, proxy 1, proxy 2, and progress). Leaf nodes are various end states (quit, success, or error). Transitions between these nodes denote user actions. 
}
\label{fig:digraph}
\end{figure*}

@@

\section{Success and Error States in Tor Launcher 5.0.3} 
\label{states} 
Here we define the end state codes that appear in Figure~\ref{fig:digraph}.
e\# and $\mbox{e\#}^\prime$ are equivalent, except that $\mbox{e\#}^\prime$ uses a bridge while e\# does not. \\

>>>>

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{torconfig.pdf}
\caption{
A digraph illustrating the potential user paths through the interface. Non-leaf nodes are screens in the user interface (first, bridge~1, bridge~2, bridge help, proxy~1, proxy~2, and progress). Leaf nodes are various end states (success or error). Transitions between these nodes denote user actions. 
}
\label{fig:digraph}
\end{figure*}

@@

\section{Success and Error States in Tor Launcher 5.0.3} 
\label{states} 
Here we define the end state codes that appear in Figure~\ref{fig:digraph}.
e\# and $\mbox{e\#}^\prime$ are equivalent, except that e\# uses a bridge while $\mbox{e\#}^\prime$ does not. \\
